### 2011-05-12 paper.tex
Fixed a statement at the end of section 3
fixed everything hopefully

\begin{remark}
For every partial function $f \in \p$, there exists another partial function $L \in \p$ such that
\begin{itemize}
\item For all $x$, $L(x) = 0$ or $L(x) = 1$.
\item If $f(x) = 1$, then $L(x) = 1$.
\item If $f(x) = 0$, then $L(x) = 0$.
\end{itemize}
\end{remark}

@@

@@

\begin{theorem}\label{amplify}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. Then \emph{$\bp \cdot C = \strongbp \cdot C$}.
\end{theorem}
Initially, this may seem to be obviously true for the same reasons that $\bp \cdot \p = \strongbp \cdot \p$. The problem is that amplification requires running some machine which accepts a language in $C$ more than once. This requires the structure of $C$ to allow for such repetitions. In particular, we will find that it is nontrivial when the $\parity$ operator is involved. This brings us to the concept of majority reductions.
\begin{definition}\label{defmajority}
We say that a complexity class $C$ is \emph{closed under majority reductions} if for any partial function $f \in C$, the partial function $\majority(f)$ defined by
$$\majority(f)(\langle x_1, \ldots, x_k\rangle) = 
\begin{cases}1 & \text{ if the number of $i$ such that }f(x_i) = 1\text{ is at least $\frac{k}{2}$} \\
0 & \text{ if the number of $i$ such that }f(x_i) = 0\text{ is more than $\frac{k}{2}$}\\
\x & \text{ otherwise}
\end{cases}$$
is in $C$.
\end{definition}
Now, we see that majority reductions are exactly what we want for amplification:
\begin{lemma}\label{majorityimpliesamplify}
If $C$ is a complexity class which is closed under majority reductions and polynomial time reductions, then \emph{$\bp \cdot C = \strongbp \cdot C$.}
\end{lemma}
\begin{proof}
This is now the same application of the Chernoff bound which shows that $\bp \cdot \p = \strongbp \cdot \p$. Suppose $f$ is a partial function in $\bp \cdot C$. Then there is a partial function $g$ in $C$ such that $\pr_y [g(\langle x,y\rangle) = 1] > 2/3$ if $f(x) = 1$ and $\pr_y [g(\langle x, y\rangle) = 0] > 2/3$ if $f(x) = 0$, where the length of $y$ is equal to $p(|x|)$ for some polynomial $p$. Let $q$ be a polynomial, where $e^{-q(|x|)}$ is the desired error probability. Let $k = 48q(|x|)$.

Here is how we determine the value $f(x)$ with error probability $e^{-q(|x|)}$. Choose $k$ strings $y_1,y_2,...,y_k$ randomly, then return $h(\langle x, y_1y_2\cdots y_k\rangle) = \majority(g)(\langle \langle x, y_1 \rangle, \langle x, y_2 \rangle, \ldots, \langle x, y_k \rangle \rangle)$. Notice that $h$ can be easily reduced to $\majority(g)$ in polynomial time, and is therefore in $C$.
Let $X_i$ be an indicator variable which is $1$ if $g(\langle x,y_i\rangle)$ agrees with $f(x)$. We have that the $X_i$ are independent Bernoulli random variables with $\pr\left[X_i = 1\right] > \frac{2}{3}$.  Then by the Chernoff bound,
\begin{align*}
\pr\left[\sum X_i < k/2\right] &= \pr\left[\sum X_i < (1 - 1/4)(2k/3)\right]\\
&< e^{-(1/4)^2 (2k/3) / 2}\\
&= e^{-q(|x|)} \\
&< 2^{-q(|x|)}
\end{align*}
We can do this for any polynomial $q$, so $f \in \strongbp \cdot C$. Hence, $\bp \cdot C = \strongbp \cdot C$. Note that if $f(x) = \x$ then we have no restrictions on what we return.
\end{proof}

Thus, in order to prove Theorem \ref{amplify}, we just need to show that any $\{\Sigma,\Pi,\bp,\parity\}$-constructible complexity class is closed under majority reductions. In order to show that these are closed under majority reductions, we will need the help of another property:
\begin{definition}\label{defintersection}
We say that a complexity class $C$ is \emph{closed under intersection} if for any partial function $f \in C$, the partial function $\intersect(f)$ defined by
$$\intersect(f)(\langle x_1, \ldots, x_k\rangle) = 
\begin{cases}1 & \text{ if $f(x_i) = 1$ for all $i$} \\
0 & \text{ if there exists some $i$ for which $f(x_i) = 0$}\\
\x & \text{ otherwise}
\end{cases}$$
is in $C$.
%We say that a class $C$ is \emph{closed under intersection} if for any language $L \in C$, the language $\intersection(L) = \{(x_1,...,x_k) : k\in\mathbb{N}, x_i \in L_i ~ \forall i\}$ is in $C$.
\end{definition}
We will demonstrate that all $\{\Sigma, \Pi, \bp, \parity\}$-constructible complexity classes are closed under intersection and under majority reductions. To do this, we will use induction on the number of operators in $C$. Clearly $\p$ is closed under intersection and majority reductions. Thus, the result follows from the following two lemmas:

@@

\begin{lemma}\label{amplifymainlemma}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. If $C$ is closed under majority reductions, then (i) \emph{$\Sigma \cdot C$}, (ii) \emph{$\Pi \cdot C$}, (iii) \emph{$\bp \cdot C$}, and (iv) \emph{$\parity \cdot C$} are all closed under majority reductions.
\end{lemma}
We begin with the proof of Lemma \ref{intersectionlemma}
\begin{proof}[Proof of Lemma \ref{intersectionlemma}]
\begin{enumerate}
\item[]
\item[(i)] Suppose $f$ is a partial function in $\Sigma\cdot C$. Then there exists a partial function $g\in C$ and a polynomial $p$ such that $f(x) = 1$ if there exists some $y$ with $|y| = p(|x|)$ such that $g(\langle x,y\rangle) = 1$, and $f(x) = 0$ if for all $y$ with $|y| = p(|x|)$ we have $g(\langle x, y\rangle) = 0$. Now, we want to show that $\intersect(f) \in \Sigma \cdot C$. Now, $\intersect(f)(\langle x_1,...,x_k\rangle) = 1$ if and only if there exist $y_1,...,y_k$ such that $g(\langle x_i, y_i\rangle) = 1$ for all $i$, which is equivalent to saying that $\intersect(g)(\langle \langle x_1,y_1\rangle,...,\langle x_k,y_k\rangle\rangle) = 1$. Similarly, $\intersect(f)(\langle x_1,...,x_k\rangle) = 0$ if and only if for all $y_1,...,y_k$, we have $\intersect(g)(\langle \langle x_1,y_1\rangle,...,\langle x_k,y_k\rangle\rangle) = 0$. Thus, $\intersect(f) \in \Sigma \cdot C$.

@@

To complete the proof of Lemma \ref{amplifymainlemma} (iv), we use the following generalization of a result in \cite{Toda}, which shows that $\parity \cdot (\p ^{\parity\cdot\p}) = \parity\cdot\p$, a fact which is used to show that $\parity \cdot \p$ is closed under majority reductions. Proving this fact is the main reason that we need the fact that the $\{\Sigma, \Pi, \bp, \parity\}$-constructible classes are closed under intersection.

\begin{theorem}\label{oracleparityc}
%Let $C$ be a class containing \emph{$\p$} which is closed under intersection. Then\linebreak \emph{$\parity \cdot (\p^{\parity \cdot C}) = \parity \cdot C$}.
Let $C$ be a class which is closed under intersection and polynomial time reductions. Then \emph{$ \p^{\parity \cdot C} = \parity \cdot C$}.
\end{theorem}
\begin{proof}
The direction $\parity \cdot C \subseteq \p^{\parity \cdot C}$ is trivial. Let us consider the interesting direction\linebreak $\p^{\parity \cdot C}\subseteq \parity\cdot C$.

Suppose $L \in \parity \cdot (P^{\parity\cdot C})$. Then, there is some polynomial time turing machine $T$, equipped with an oracle to some language $M \in \parity\cdot C$, which accepts $x$ if and only if $x\in L$.

To show that $L$ lies in $\parity\cdot C$, the basic idea is to ``guess" the answers to the oracle calls, and then check them. We make it so that we get an odd number of solutions whenever we guess correctly, and an even number of solutions otherwise.

@@

Each oracle call queries some input to check if it is $M$. There is a language $P \in C$ such that $M$ accepts $x$ if and only if $P$ accepts $(x,y)$ for an odd number of $y$, where $|y| = r(|x|)$ for some polynomial $r$.

To show that $L$ is in $\parity \cdot C$, we guess the following bits for a given input $x$:
\begin{itemize}
\item Bits $a_1,a_2,...,a_{p(|x|)}$. Intuitively, these will be the answers to the oracle calls made by $T$.
\item Bits $b_1,b_2,...,b_{p(|x|)}$. The purpose of these will become clear later.
\item Strings $y_1,y_2,...,y_{p(|x|)}$, each of length $r(q(|x|))$. These are the strings that an oracle call guesses.
\end{itemize}
After guessing, we do the following polynomial time reduction to $C$. For an input $x$, simulate $T$ using the bits $a_1,a_2,...,a_{p(|x|)}$ as the answers to the oracle calls (taking $1$ to mean that the oracle call accepted, and $0$ to mean that the oracle call rejected). If $T$ would reject, then reject.

Also find the strings $x_1,x_2,...,x_{p(|x|)}$ which are the inputs that $T$ would query to the oracles. These may depend on the $a_i$. We now want to verify that the oracle calls are correct. Say that $(a_i, b_i, y_i)$ is \emph{good} if either
\begin{itemize}
\item $b_i = 0$, and both $a_i = 0$ and $y_i = 0^{r(q(|x|))}$, or
\item $b_i = 1$ and $P$ accepts $(x_i, y_i)$
\end{itemize}
Reject if any $(a_i, b_i, y_i)$ is not good. To determine if they are all good, we will have to check some pairs $(x_i, y_i)$ to see if $P$ accepts them. We can do this with a call to $\intersect(P)$, which is in $C$ since $C$ is closed under intersection.

@@

Why does this give us what we want? We want to show that this will accept for an odd number of choices of the $a_i$, $b_i$, and $y_i$ if and only if $x \in L$. Let $\# (a_1,...,a_{p(|x|)})$ be the number of ways to choose the $b_i$, and $y_i$ such that all triples $(a_i,b_i,y_i)$ are good. Then the total number of accepting paths is
\begin{center}$\displaystyle \sum_{a_1,...,a_{p(|x|)}\text{ such that $T$ accepts}}  \#(a_1,...,a_{p(|x|)})$\end{center}
We claim that $ \#(a_1,...,a_{p(|x|)})$ is odd if and only if $a_1,a_2,...,a_{p(|x|)}$ are the correct answers to the oracle calls. This follows from the way we chose to decide if $(a_i, b_i, y_i)$ is good. If $a_1,a_2,...,a_{p(|x|)}$ are the correct answers to the oracle calls, then for each $i$, there are an odd number of $(b_i,y_i)$ such that $(a_i, b_i, y_i)$ is good. If $a_i = 1$, all good triples will have $b_i = 1$, so the parity is determined by the number of $y_i$ for which $P$ accepts $(x_i, y_i)$. But if $a_i = 1$, then this should be odd. If $a_i = 0$, then the number of $y_i$ for which $P$ accepts $(x_i, y_i)$ is even. However, we get one more good pair, namely $(0,0,0)$.

@@

Hence, the sum will be odd if and only if $T$ accepts when the oracle calls are correct. Therefore, $L$ accepts $x$ if and only if this accepts for an odd number of choices of all the $a_i$, $b_i$, and $y_i$, and $L$ rejects $x$ otherwise. Thus, $L \in \parity \cdot C$. This is true for any $L \in \p^{\parity \cdot C}$, so $\p^{\parity \cdot C} \subseteq \parity \cdot C$.
\end{proof}
\begin{remark}\emph{
While this paper applies Theorem \ref{oracle} only in the case where $C$ is $\{\Sigma,\Pi,\bp,\parity\}$-constructible, it can also be used to show, for instance, that $\p^{\parity \cdot \pp} = \parity \cdot \pp$, although it is nontrivial to show that $\pp$ is closed under intersection. For a proof, see \cite{Beigel}.
}\end{remark}

We can use this remarkable fact to finish the proof of Lemma \ref{amplifymainlemma}, thus proving Theorem \ref{amplify}.
\begin{proof}[Proof of Lemma \ref{amplifymainlemma} (iv)]
Take any language $L \in \parity \cdot C$. We want to show that $\majority(L)$ is in $\parity \cdot C$. It is easy to see that $\majority(L) \in \p^{\parity \cdot C}$. For a given $k$-tuple $(x_1,x_2,...,x_k)$, we use the oracle call to $\parity \cdot C$ to determine how many of the $x_i$ are accepted in $L$, and how many are rejected. If more than half are accepted, we accept, and if more than half are rejected, we reject.

Thus, $\majority(L) \in \p^{\parity \cdot C}$. But we know that $C$ is closed under intersection and under polynomial reductions. Thus, we can apply Theorem \ref{oracleparityc} to get that $\p^{\parity \cdot C} = \parity \cdot C$. Hence, $\majority(L) \in \parity \cdot C$. Therefore $\parity \cdot C$ is closed under majority reductions.
\end{proof}

@@

\bibitem{Beigel} Beigel, R., Reingold, N., and Spielman, D.A. \emph{PP is closed under intersection}, Proceedings of ACM Symposium on Theory of Computing 1991, pp. 1-9, 1991.

>>>>

\begin{remark}\label{equivtoold}\emph{
For every partial function $f \in \p$, there exists another partial function $L \in \p$ such that
\begin{itemize}
\item For all $x$, $L(x) = 0$ or $L(x) = 1$.
\item If $f(x) = 1$, then $L(x) = 1$.
\item If $f(x) = 0$, then $L(x) = 0$.
\end{itemize}
}\end{remark}

@@

\begin{definition}
We say that a complexity class $C$ is \emph{well-structured} if it is $\{\Sigma, \Pi, \bp, \parity\}$-constructible, and the operator $\parity$ does not appear to the left of a $\bp$ operator.
\end{definition}

@@

\begin{theorem}\label{amplify}
Let $C$ be a well-structured complexity class. Then \emph{$\bp \cdot C = \bp \parity C$}.
\end{theorem}

Initially, this may seem to be obviously true for the same reasons that $\bp \cdot \p = \strongbp \cdot \p$. The problem is that amplification requires running some machine which accepts a language in $C$ more than once. This requires the structure of $C$ to allow for such repetitions. In particular, we will find that it is nontrivial when the $\parity$ operator is involved. This brings us to the concept of majority reductions.
\begin{definition}\label{defmajority}
We say that a complexity class $C$ is \emph{closed under majority reductions} if for any partial function $f \in C$, the partial function $\majority(f)$ defined by
$$\majority(f)(\langle x_1, \ldots, x_k\rangle) = 
\begin{cases}1 & \text{ if the number of $i$ such that }f(x_i) = 1\text{ is at least $\frac{k}{2}$} \\
0 & \text{ if the number of $i$ such that }f(x_i) = 0\text{ is more than $\frac{k}{2}$}\\
\x & \text{ otherwise}
\end{cases}$$
is in $C$.
\end{definition}
Now, we see that majority reductions are exactly what we want for amplification:
\begin{lemma}\label{majorityimpliesamplify}
If $C$ is a complexity class which is closed under majority reductions and polynomial time reductions, then \emph{$f\in\strongbp \cdot C$.}
\end{lemma}
\begin{proof}
This is now the same application of the Chernoff bound which shows that $\bp \cdot \p = \strongbp \cdot \p$. Suppose $f$ is a partial function in $\bp \cdot C$. Then there is a partial function $g$ in $C$ such that $\pr_y [g(\langle x,y\rangle) = 1] > 2/3$ if $f(x) = 1$ and $\pr_y [g(\langle x, y\rangle) = 0] > 2/3$ if $f(x) = 0$, where the length of $y$ is equal to $p(|x|)$ for some polynomial $p$. Let $q$ be a polynomial, where $e^{-q(|x|)}$ is the desired error probability. Let $k = 48q(|x|)$.

Here is how we determine the value $f(x)$ with error probability $e^{-q(|x|)}$. Choose $k$ strings $y_1,y_2,...,y_k$ randomly, then return $h(\langle x, y_1y_2\cdots y_k\rangle) = \majority(g)(\langle \langle x, y_1 \rangle, \langle x, y_2 \rangle, \ldots, \langle x, y_k \rangle \rangle)$. Notice that $h$ can be easily reduced to $\majority(g)$ in polynomial time, and is therefore in $C$.
Let $X_i$ be an indicator variable which is $1$ if $g(\langle x,y_i\rangle)$ agrees with $f(x)$. We have that the $X_i$ are independent Bernoulli random variables with $\pr\left[X_i = 1\right] > \frac{2}{3}$.  Then by the Chernoff bound,
\begin{align*}
\pr\left[\sum X_i < k/2\right] &= \pr\left[\sum X_i < (1 - 1/4)(2k/3)\right]\\
&< e^{-(1/4)^2 (2k/3) / 2}\\
&= e^{-q(|x|)} \\
&< 2^{-q(|x|)}
\end{align*}
We can do this for any polynomial $q$, so $f \in \strongbp \cdot C$. Thus, $\bp \cdot C = \strongbp \cdot C$.
\end{proof}

Thus, in order to prove Theorem \ref{amplify}, we just need to show that any well-structured complexity class is closed under majority reductions. In order to show that these are closed under majority reductions, we will need the help of another property:
\begin{definition}\label{defintersection}
We say that a complexity class $C$ is \emph{closed under intersection} if for any partial function $f \in C$, the partial function $\intersect(f)$ defined by
$$\intersect(f)(\langle x_1, \ldots, x_k\rangle) = 
\begin{cases}1 & \text{ if $f(x_i) = 1$ for all $i$} \\
0 & \text{ if there exists some $i$ for which $f(x_i) = 0$}\\
\x & \text{ otherwise}
\end{cases}$$
is in $C$.
%We say that a class $C$ is \emph{closed under intersection} if for any language $L \in C$, the language $\intersection(L) = \{(x_1,...,x_k) : k\in\mathbb{N}, x_i \in L_i ~ \forall i\}$ is in $C$.
\end{definition}
We will demonstrate that all well-structured complexity classes are closed under intersection and under majority reductions. To do this, we will use induction on the number of operators in $C$. Clearly $\p$ is closed under intersection and majority reductions. Thus, the result follows from the following two lemmas:

@@

\begin{lemma}\label{amplifymainlemma}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class class. If $C$ is closed under majority reductions, then (i) \emph{$\Sigma \cdot C$}, (ii) \emph{$\Pi \cdot C$}, and (iii) \emph{$\bp \cdot C$} are closed under majority reductions. Furthermore, (iv) \emph{$\parity \cdot C$} is closed under majority reductions if $C$ is $\{\Sigma, \Pi, \parity\}$-constructible.
\end{lemma}
We begin with the proof of Lemma \ref{intersectionlemma}
\begin{proof}[Proof of Lemma \ref{intersectionlemma}]
\begin{enumerate}
\item[]
\item[(i)] Suppose $f$ is a partial function in $\Sigma\cdot C$. Then there exists a partial function $g\in C$ and a polynomial $p$ such that $f(x) = 1$ if there exists some $y$ with $|y| = p(|x|)$ such that $g(\langle x,y\rangle) = 1$, and $f(x) = 0$ if for all $y$ with $|y| = p(|x|)$ we have $g(\langle x, y\rangle) = 0$. Now, we want to show that $\intersect(f) \in \Sigma \cdot C$. Now, $\intersect(f)(\langle x_1,...,x_k\rangle) = 1$ if and only if there exist $y_1,...,y_k$ such that $g(\langle x_i, y_i\rangle) = 1$ for all $i$, which is equivalent to saying that $\intersect(g)(\langle \langle x_1,y_1\rangle,...,\langle x_k,y_k\rangle\rangle) = 1$. Similarly, $\intersect(f)(\langle x_1,...,x_k\rangle) = 0$ if and only if for all $y_1,...,y_k$, we have $\intersect(g)(\langle \langle x_1,y_1\rangle,...,\langle x_k,y_k\rangle\rangle) = 0$. Thus, $\intersect(f) \in \Sigma \cdot C$.

@@

To complete the proof of Lemma \ref{amplifymainlemma} (iv), we use the following generalization of a result in \cite{Toda}, which is that $\parity \cdot (\p ^{\parity\cdot\p}) = \parity\cdot\p$, a fact which is used to show that $\parity \cdot \p$ is closed under majority reductions. Proving this fact is the main reason that we need the fact that the $\{\Sigma, \Pi, \bp, \parity\}$-constructible classes are closed under intersection.

\begin{theorem}\label{oracleparityc}
%Let $C$ be a class containing \emph{$\p$} which is closed under intersection. Then\linebreak \emph{$\parity \cdot (\p^{\parity \cdot C}) = \parity \cdot C$}.
%Let $C$ be a $\{\Sigma,\Pi,\parity\}$-constructible class. Then \emph{$ \p^{\parity \cdot C} = \parity \cdot C$}.
Let $C$ be a class containing \emph{$\p$} which is closed under intersection and such that every function in $C$ is defined everywhere (no \emph{$\x$}'s). Then \emph{$ \p^{\parity \cdot C} = \parity \cdot C$}.
\end{theorem}
\begin{proof}
The direction $\parity \cdot C \subseteq \p^{\parity \cdot C}$ is trivial. Let us consider the interesting direction\linebreak $\p^{\parity \cdot C}\subseteq \parity\cdot C$.

Suppose $f \in \parity \cdot (P^{\parity\cdot C})$. Then, there is some polynomial time turing machine $T$, equipped with an oracle to some function $g\in \parity\cdot C$, which accepts $x$ if $f(x) = 1$ and rejects $x$ if $f(x) = 0$.

To show that $f$ lies in $\parity\cdot C$, the basic idea is to ``guess" the answers to the oracle calls, and then check them. We make it so that we get an odd number of solutions whenever we guess correctly, and an even number of solutions otherwise.

@@

Each oracle call queries some input to check if it is $g$. There is a function $h \in C$ and a polynomial $r$ such that $g(x) = 1$ if and only if $h(\langle x,y\rangle) = 1$ for an odd number of $y\in\{0,1\}^{r(|x|)}$, and $g(x) = 0$ otherwise. Thus, $f \in \parity \cdot C$.

To show that $f$ is in $\parity \cdot C$, we guess the following bits for a given input $x$:
\begin{itemize}
\item Bits $a_1,a_2,...,a_{p(|x|)}$. Intuitively, these will be the answers to the oracle calls made by $T$.
\item Bits $b_1,b_2,...,b_{p(|x|)}$. The purpose of these will become clear later.
\item Strings $y_1,y_2,...,y_{p(|x|)}$, each of length $r(q(|x|))$. These are the strings that an oracle call guesses.
\end{itemize}
After guessing, we do the following polynomial time reduction to $\intersect(h)$. For an input $x$, simulate $T$ using the bits $a_1,a_2,...,a_{p(|x|)}$ as the answers to the oracle calls (taking $1$ to mean that the oracle call accepted, and $0$ to mean that the oracle call rejected). If $T$ would reject, then reject.

Also find the strings $x_1,x_2,...,x_{p(|x|)}$ which are the inputs that $T$ would query to the oracles. These may depend on the $a_i$. We now want to verify that the oracle calls are correct. Say that $(a_i, b_i, y_i)$ is \emph{good} if either
\begin{itemize}
\item $b_i = 0$, and both $a_i = 0$ and $y_i = 0^{r(q(|x|))}$, or
\item $b_i = 1$ and $h(x_i, y_i)$
\end{itemize}
Reject if any $(a_i, b_i, y_i)$ is not good. To determine if they are all good, we will have to check some pairs $(x_i, y_i)$ to see if $\overline{h}(x_i,y_i) = 1$. We can do this with a call to $\intersect(h)$.

@@

Why does this give us what we want? We want to show that this will accept for an odd number of choices of the $a_i$, $b_i$, and $y_i$ if and only if $f(x) = 1$. Let $\# (a_1,...,a_{p(|x|)})$ be the number of ways to choose the $b_i$, and $y_i$ such that all triples $(a_i,b_i,y_i)$ are good. Then the total number of accepting paths is
\begin{center}$\displaystyle \sum_{a_1,...,a_{p(|x|)}\text{ such that $T$ accepts}}  \#(a_1,...,a_{p(|x|)})$\end{center}
We claim that $ \#(a_1,...,a_{p(|x|)})$ is odd if and only if $a_1,a_2,...,a_{p(|x|)}$ are the correct answers to the oracle calls. This follows from the way we chose to decide if $(a_i, b_i, y_i)$ is good. If $a_1,a_2,...,a_{p(|x|)}$ are the correct answers to the oracle calls, then for each $i$, there are an odd number of $(b_i,y_i)$ such that $(a_i, b_i, y_i)$ is good. If $a_i = 1$, all good triples will have $b_i = 1$, so the parity is determined by the number of $y_i$ for which $P$ accepts $(x_i, y_i)$. But if $a_i = 1$, then this should be odd. If $a_i = 0$, then the number of $y_i$ for which $P$ accepts $(x_i, y_i)$ is even. However, we get one more good pair, namely $(0,0,0)$.

@@

Hence, the sum will be odd if and only if $T$ accepts when the oracle calls are correct. Therefore, $f(x) = 1$ if and only if this accepts for an odd number of choices of all the $a_i$, $b_i$, and $y_i$.

%Hence, the sum will be odd if and only if $T$ accepts when the oracle calls are correct. Therefore, $L$ accepts $x$ if and only if this accepts for an odd number of choices of all the $a_i$, $b_i$, and $y_i$, and $L$ rejects $x$ otherwise. Thus, $L \in \parity \cdot C$. This is true for any $L \in \p^{\parity \cdot C}$, so $\p^{\parity \cdot C} \subseteq \parity \cdot C$.
\end{proof}
%\begin{remark}\emph{
%While this paper applies Theorem \ref{oracle} only in the case where $C$ is $\{\Sigma,\Pi,\bp,\parity\}$-constructible, it can also be used to show, for instance, that $\p^{\parity \cdot \pp} = \parity \cdot \pp$, although it is nontrivial to show that $\pp$ is closed under intersection. For a proof, see \cite{Beigel}.
%}\end{remark}

We can use this remarkable fact to finish the proof of Lemma \ref{amplifymainlemma}, thus proving Theorem \ref{amplify}.
\begin{proof}[Proof of Lemma \ref{amplifymainlemma} (iv)]
Take any function $f \in \parity \cdot C$. If $C$ is $\{\Sigma, \Pi, \parity\}$-constructible, we can assume that $f$ is defined everywhere; any function not defined everywhere can be extended to a function which is, simply by extending the innermost $\p$ function (see Remark \ref{equivtoold}).

We want to show that $\majority(f)$ is in $\parity \cdot C$. It is easy to see that $\majority(f) \in \p^{\parity \cdot C}$. For a given $k$-tuple $(x_1,x_2,...,x_k)$, we use the oracle call to $\parity \cdot C$ to determine how many of the $x_i$ are accepted in $L$, and how many are rejected. If at least half are accepted, we accept, and if more than half are rejected, we reject.

Thus, $\majority(f) \in \p^{\parity \cdot C}$. Thus, we can apply Theorem \ref{oracleparityc} to get that $\majority(f) \in \parity \cdot C$. Therefore $\parity \cdot C$ is closed under majority reductions.
\end{proof}

@@

%\bibitem{Beigel} Beigel, R., Reingold, N., and Spielman, D.A. \emph{PP is closed under intersection}, Proceedings of ACM Symposium on Theory of Computing 1991, pp. 1-9, 1991.
